### 2019-04-16 papers/haskell19/4-generators.tex
WIP

\begin{code}
instance BArbitrary1 f => BArbitrary1 (f otimes n) where
  liftBGen gen lvl = Freq <$> liftBGen gen lvl

instance BArbitrary1 f => BArbitrary1 (Term f) where
  liftBGen gen lvl = Term <$> liftBGen gen lvl
\end{code}

@@

\begin{code}
instance (BArbitrary1 f, BArbitrary1 g)
  => BArbitrary1 (f oplus g) where
  liftBGen gen lvl =
    if lvl > 0
    then frequency
      [ (freqVal  at(FreqOf f) ,  InL <$> liftBGen gen lvl)
      , (freqVal  at(FreqOf g) ,  InR <$> liftBGen gen lvl) ]
    else frequency
      [ (freqVal  at(FreqOf' f) ,  InL <$> liftBGen gen lvl)
      , (freqVal  at(FreqOf' g) ,  InR <$> liftBGen gen lvl) ]
\end{code}

\begin{code}
instance BArbitrary1 Con_Text where
  liftBGen gen lvl = Con_Text <$> arbitrary

instance BArbitrary1 Con_Sing where
  liftBGen gen lvl = Con_Sing <$> arbitrary

instance BArbitrary1 Con_Tag where
  liftBGen gen lvl = Con_Tag <$> arbitrary <*> gen (lvl - 1)

instance BArbitrary1 Con_Join where
  liftBGen gen lvl = Con_Join <$> gen (lvl - 1) <*> gen (lvl - 1)
\end{code} %$

\begin{code}
instance BArbitrary1 Fun_br where
  liftBGen gen lvl = pure Fun_br

instance BArbitrary1 Fun_bold where
  liftBGen gen lvl = Fun_bold <$> gen (lvl - 1)

instance BArbitrary1 Fun_cat where
  liftBGen gen lvl = Fun_cat <$> gen (lvl - 1) <*> gen (lvl - 1)

instance BArbitrary1 Fun_list where
  liftBGen gen lvl = Fun_list <$> liftGen (gen (lvl - 1))
\end{code} %$

\begin{code}
instance BArbitrary1 Pat_simplify_1 where
  liftBGen gen lvl
    = Pat_simplify_1 <$> arbitrary <*> arbitrary

instance BArbitrary1 Pat_simplify_2 where
  liftBGen gen lvl
    = Pat_simplify_2 <$> gen (lvl - 1) <*> gen (lvl - 1)
\end{code}

\begin{code}
instance BArbitrary1 f => BArbitrary (Fix f) where
  bounded lvl = Fix <$> liftBGen bounded lvl
\end{code} %$

\begin{code}
genFix  ::  forall f dot BArbitrary1 f =>  BGen (Fix f)
genFix lvl = bounded at(Fix f) lvl
\end{code}

\begin{code}
genEval :: forall f a dot (BArbitrary1 f, Algebra f a) => BGen a
genEval lvl = eval <$> genFix at f lvl
\end{code} %$

>>>>

\begin{code}
instance BArbitrary1 f => BArbitrary1 (f otimes n) where
  liftBGen gen d = Freq <$> liftBGen gen d

instance BArbitrary1 f => BArbitrary1 (Term f) where
  liftBGen gen d = Term <$> liftBGen gen d
\end{code}

@@

\begin{code}
instance (BArbitrary1 f, BArbitrary1 g)
  => BArbitrary1 (f oplus g) where
  liftBGen gen d =
    if d > 0
    then frequency
      [ (freqVal  at(FreqOf f) ,  InL <$> liftBGen gen d)
      , (freqVal  at(FreqOf g) ,  InR <$> liftBGen gen d) ]
    else frequency
      [ (freqVal  at(FreqOf' f) ,  InL <$> liftBGen gen d)
      , (freqVal  at(FreqOf' g) ,  InR <$> liftBGen gen d) ]
\end{code}

\begin{code}
freqVal :: forall n dot KnownNat n => Int
\end{code}

\begin{code}
instance BArbitrary1 Con_Text where
  liftBGen gen d = Con_Text <$> arbitrary

instance BArbitrary1 Con_Sing where
  liftBGen gen d = Con_Sing <$> arbitrary

instance BArbitrary1 Con_Tag where
  liftBGen gen d = Con_Tag <$> arbitrary <*> gen (d - 1)

instance BArbitrary1 Con_Join where
  liftBGen gen d = Con_Join <$> gen (d - 1) <*> gen (d - 1)
\end{code} %$

\begin{code}
instance BArbitrary1 Fun_br where
  liftBGen gen d = pure Fun_br

instance BArbitrary1 Fun_bold where
  liftBGen gen d = Fun_bold <$> gen (d - 1)

instance BArbitrary1 Fun_cat where
  liftBGen gen d = Fun_cat <$> gen (d - 1) <*> gen (d - 1)

instance BArbitrary1 Fun_list where
  liftBGen gen d = Fun_list <$> liftGen (gen (d - 1))
\end{code} %$

\begin{code}
instance BArbitrary1 Pat_simplify_1 where
  liftBGen gen d
    = Pat_simplify_1 <$> arbitrary <*> arbitrary

instance BArbitrary1 Pat_simplify_2 where
  liftBGen gen d
    = Pat_simplify_2 <$> gen (d - 1) <*> gen (d - 1)
\end{code}

\begin{code}
instance BArbitrary1 f => BArbitrary (Fix f) where
  bounded d = Fix <$> liftBGen bounded d
\end{code} %$

\begin{code}
genFix  ::  forall f dot BArbitrary1 f =>  BGen (Fix f)
genFix d = bounded at(Fix f) d
\end{code}

\begin{code}
genEval :: forall f a dot (BArbitrary1 f, Algebra f a) => BGen a
genEval d = eval <$> genFix at f d
\end{code} %$

### 2019-04-16 papers/haskell19/5-typelevel.tex
WIP

@@

@@

\begin{code}
type family (t :: * -> *) apply (a :: *) :: * -> *  where
  (Some t)      apply  a  = t a
  (f oplus g)   apply  a  = (f apply a) oplus (g apply a)
  (f otimes n)  apply  a  = (f apply a) otimes n
  (Term t)      apply  a  = Term (t apply a)
  t             apply  a  = t
\end{code}

\begin{code}
type Con' a    = Term  (Con a)
type Fun' a    = Term  (Fun a)
type Pat' a n  = Term  (Pat a n)
\end{code}

\begin{code}
instance Arbitrary Html where
  arbitrary = sized (genEval at Html_Spec)
\end{code}

>>>>

\begin{code}
instance BArbitrary Html where
  bounded = genEval at Html_Spec

instance Arbitrary Html where
  arbitrary = sized bounded
\end{code}

@@

\begin{code}
type Con' a    = Term  (Con a)
type Pat' a n  = Term  (Pat a n)
type Fun' a    = Term  (Fun a)
\end{code}

\begin{code}
data Tree a = Leaf a | Node (Tree a) (Tree a)
\end{code}

\begin{code}
data Con_Leaf a r = Con_Leaf a
data Con_Node a r = Con_Node r r
\end{code}

\begin{code}
instance Algebra (Con_Leaf a) (Tree a) where ...
instance Algebra (Con_Node a) (Tree a) where ...
\end{code}

\begin{code}
instance Arbitrary a => BArbitrary1 (Con_Leaf a) where ...
instance Arbitrary a => BArbitrary1 (Con_Node a) where ...
\end{code}

@@

\begin{code}
type instance Con "Leaf" = Some Con_Leaf
type instance Con "Node" = Some Con_Node
\end{code}

\begin{code}
type Tree_Spec
  =      Con "Leaf" otimes 2
  oplus  Con "Node" otimes 3
\end{code}

\begin{code}
type family (f :: * -> *) apply (a :: *) :: * -> *  where
  (Some f)      apply  a  = f a
  (f oplus g)   apply  a  = (f apply a) oplus (g apply a)
  (f otimes n)  apply  a  = (f apply a) otimes n
  (Term f)      apply  a  = Term (t apply a)
  f             apply  a  = f
\end{code}

\begin{code}
instance Arbitrary a => BArbitrary (Tree a) where
  bounded = genEval at (Tree_Spec apply a)
\end{code}
